Wigglyhedra

### 2024-06-12 draft/wigglyhedra.tex

\subsection{Categorical constraints on compatibility of curves}
In this section, we give a categorical criterion for two wiggly arcs to be compatible as in~\cref{def:compatible}.
As such, this section is somewhat dual to the previous section --- the criterion in this section determines whether a pair of wiggly arcs can belong together in a single wiggly pseudotriangulation, whereas the previous section generated a wiggly pseudotriangulation given any object of the category.
\begin{proposition}
  Consider two wiggly arcs \(\alpha\) and \(\alpha'\), and let \(X\) and \(X'\) be objects in the standard heart \(\mathcal{A}_m\) corresponding to \(\alpha\) and \(\alpha'\) respectively.
  Then \(\alpha\) and \(\alpha'\) are compatible in the sense of~\cref{def:compatible} if and only if \(\Ext^1(X\langle g \rangle, X\langle g' \rangle) = 0\) for any two integers \(g\) and \(g'\).
\end{proposition}
\begin{proof}
  \asilata{TODO.}
\end{proof}
\begin{remark}
  This proposition is similar to the condition of being compatible in a cluster-tilting object.
  \asilata{Expand and make precise.}
\end{remark}
\begin{remark}
  As stated, this proposition is not expected to be true in greater generality.
  For instance, it does not hold for the zigzag algebra of Dynkin type~$D_4$.
  However, we expect to see similar constraints on compatibility, which we hope to turn to in forthcoming work.
  \asilata{Decide what to say here, because the forthcoming work is far from complete, although I do have counterexamples in type \(D_4\). Discussing how to interpret these counterexamples may not involve too much more work?}
\end{remark}
\begin{question}
  How to best relate this section to the previous one purely categorically?
  That is, given the categorical constraint on compatibility of arcs, is it also clear that it gives a constraint on objects appearing in the cohomology filtration?
  \asilata{Make more precise.}
\end{question}

>>>>

\subsection{Categorical constraints on compatibility of curves}
In this section, we give a categorical criterion for two wiggly arcs to be compatible as in~\cref{def:compatible}.
As such, this section is somewhat dual to the previous section --- the criterion in this section determines whether a pair of wiggly arcs can belong together in a single wiggly pseudotriangulation, whereas the previous section generated a wiggly pseudotriangulation given any object of the category.
\begin{proposition}
  Consider two wiggly arcs \(\alpha\) and \(\alpha'\), and let \(X\) and \(X'\) be objects in the standard heart \(\mathcal{A}_m\) corresponding to \(\alpha\) and \(\alpha'\) respectively.
  Then \(\alpha\) and \(\alpha'\) are compatible in the sense of~\cref{def:compatible} if and only if \(\Ext^1(X, X') = 0\).
\end{proposition}
\begin{proof}
  \asilata{TODO.}
\end{proof}
\begin{remark}
  This proposition is similar to the condition of being compatible in a cluster-tilting object.
  \asilata{Expand and make precise.}
\end{remark}
\begin{remark}
  As stated, this proposition is not expected to be true in greater generality.
  For instance, it does not hold for the zigzag algebra of Dynkin type~$D_4$.
  However, we expect to see similar constraints on compatibility, which we hope to turn to in forthcoming work.
  \asilata{Decide what to say here, because the forthcoming work is far from complete, although I do have counterexamples in type \(D_4\). Discussing how to interpret these counterexamples may not involve too much more work?}
\end{remark}
\begin{question}
  How to best relate this section to the previous one purely categorically?
  That is, given the categorical constraint on compatibility of arcs, is it also clear that it gives a constraint on objects appearing in the cohomology filtration?
  \asilata{Make more precise.}
\end{question}

\asilata{Write something about \(g\)-vectors.}
